--- 
title: "IMOP: Workflowr Quick Start"
author: "Ania Tassinari & Caitlin Guccione"
date: "Summer 2019"
geometry: margin=2cm
site: bookdown::bookdown_site
#output: bookdown::gitbook
bookdown::gitbook:
  config:
    fontsettings:
      theme: Night
documentclass: article
classoption: openany
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
split_by: "chapter+number"
always_allow_html: yes
new_session: yes
urlcolor: blue
---

# Set Up 

In the `Console` tab of RStudio make sure you are in `(None)` project: 

```{r setUp, eval=FALSE }
install.packages("workflowr")
library("workflowr")
wflow_git_config(user.name = "First Last", user.email = "first.last@agios.com")
```

# Creating Projects

In the `Console` tab, 

```{r createProj, create, eval=FALSE }
wflow_start("PROJECT")
wflow_build()
wflow_publish(c("analysis/*.Rmd"), "Publish the initial files for PROJECT")
```

# Connecting to GitLab

In the `Console` tab, 

```{r git, eval=FALSE}
wflow_use_gitlab(username = "first.last", repository = "PROJECT", domain = "git.agios.local")
```

Go to your Agios GitLab and do the following:

+ Create a project in GitLab with the same name as the project in RStudio
+ Select all the text in the `push an existing Git repository option`
+ Make sure you are in PROJECT directory and paste into `Terminal`

# Creating a New File

In the `Console` tab, 

```{r newFile, eval=FALSE}
wflow_open("analysis/NEW_FILE.Rmd")
wflow_build()
wflow_publish(c("analysis/*.Rmd"), "Publish the file NEW_FILE")
```

In the `Terminal` tab, 
```{r gitPush, eval=FALSE}
git push
```


