--- 
title: "IMOP: Workflowr Quick Start"
author: "Ania Tassinari & Caitlin Guccione"
date: "Summer 2019"
geometry: margin=2cm
site: bookdown::bookdown_site
bookdown::pdf_document:
    includes:
      in_footer: footer.tex
bookdown::gitbook:
  config:
    fontsettings:
      theme: Night
documentclass: article
classoption: openany
link-citations: yes
split_by: "chapter+number"
always_allow_html: yes
new_session: yes
urlcolor: blue
---

# Set Up - Once Per Machine

It is ideal to do this setup in RStudio, but any platform of R will work: 

```{r setUp, eval=FALSE }
install.packages("workflowr")
library("workflowr") # Loads the workflowr package
wflow_git_config(user.name = "First Last", user.email = "first.last@agios.com")
```

# Create Project 

## R Prep

```{r createRProj, create, eval=FALSE }
library("workflowr") # Don't have to repeat if completed above
wflow_start("/path/to/PROJECT") # Sets up the folder structure, RStudio project & a .git repo
```

## GitLab Repo Connection

Go to your Agios GitLab and do the following:

+ Create a project in GitLab with the same name as the project in RStudio
+ Go to your PROJECT directory in your `terminal` & paste `Push an Existing Git Repository`

## Complete connection in R

```{r createGitProj, create, eval=FALSE }
wflow_build() # Builds Rmd files to HTML which creates the site allowing you to preview changes
wflow_publish(files=c("analysis/*.Rmd"), message="Publish initial files") 
# Builds Rmd files to HTML then, commits both Rmd & HTML files to GitLab with the above message
# JavaScriptt/CSS files, which style the webpage are automatically commited as well
$ git push # Pushes webpage to GitLab which saves a backup & allows others to view
wflow_use_gitlab(username = "first.last", domain = "git.agios.local")
# Creates a link on the home page of your website to your source code on GitLab
```

# Creating a New File & Running Analysis

```{r newFile, eval=FALSE}
wflow_open("analysis/NEW.Rmd") # Creates & opens a new file
wflow_build() # Equivalent to RStudio's 'Knit' button
wflow_publish(files=c("analysis/NEW.Rmd"), message ="Publish the file NEW") 
$ git push # Pushes webpage to Git which saves a backup & allows others to view
```

Repeat this process anytime you want to update your page. 

$ Make sure you are in your `terminal` under the correct project before running the `git push` command
